Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-24 lloveras_2020.tex
acomodando graficos

\section{Results}\label{resu} 
\subsection{Tomographic Results}\label{demt_res} 
A) Carrington (Lat/Lon) maps of the DEMT products Ne and Te at selected heights 1.025, 1.105, 1.205 Rsun, over plotting the Open/Closed (O/C) boundary from the AWSoM model. This plot gives initial CONTEXT.

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ $1.105\,\mrsun$, respectively. Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
\label{carmaps_demt_2208}
\end{center}
\end{figure}

B)    I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

@@

Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green). This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel). Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
\label{rpoint_demt}
\end{center}
\end{figure}

C) A plot of the average DEMT Ne(r) along all field lines of type I (in solid-blue), of type II (in solid-red and of type III (in solid-green). Over plotted in the same color code but in dashed-line style the AWSoM results along the same three statistical sample of field-lines. In particular, this shows the global 3D agreement between AWSoM and DEMT in distinct magnetic structures and carefully tracing along field lines

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{A plot of the average $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
\label{rpoint}
\end{center}
\end{figure}

D) Same as C) but for Te.

C) and D) will be complemented with companion histograms showing in a statistical fashion how AWSoM and DEMT results compare.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{
{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}
}
\label{histos_2082}
\end{center}
\end{figure}

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
\caption{Same as Figure \ref{histos_2082} but for CR2208.}
\label{histos_2208}
\end{center}
\end{figure}

@@

\begin{figure}%[h]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged of DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM.}
\label{perf_lon_vr}
\end{center}
\end{figure}

>>>>

For both rotations, the DEMT AWSoM 3D maps of electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were traced along the magnetic field lines modeled with AWSoM as described at the end of Section \ref{awsom}. In the case of closed loops, results were separated into their two {legs}, defined as the two segments that go from the coronal base up to the apex.

Se eligen loops con $abs(person_temp) mayor a .5$ lo cual nos permite descartar loops QI.
OBS: Esto es valido para hasta la fig 7 inclusive.

For each open field line, and for each leg of the closed ones, an exponential fit was then applied to the $N_e(r)$ data points, and a linear fit applied to the $T_m(r)$ data points, as described by

\begin{eqnarray}
N_e &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]},\label{Nfit}\\
T_\textrm{m} &=& a\,r\,+\,b,\label{Tfit}
\end{eqnarray}

\noindent
where $h \equiv r - 1\,\mrsun$, and $a$ and $b$ are constants.

In the case of the electron density, the fitted function corresponds to the isothermal hydrostatic equilibrium solution, allowing for variation of the solar gravitational acceleration with height. After computing the footpoint ($r=1.0\,\mrsun$) electron density $N_{0}\,[\cm^{-3}]$ and scale height $\lN\,[\mrsun]$, this choice of function provides a straightforward means to directly evaluate how compatible is the observed coronal thermodynamical state with the hydrostatic solution, as analyzed in Section \ref{qi}. In the case of the DEMT electron mean temperature, the linear fit allows characterization of its variation with height by means of a characteristic temperature gradient $a = \textrm{d}T_m/\textrm{d}r\,[\MK/\mrsun]$ along each leg/loop.

*Nos quedamos con los fiteos que cumplen test de hipotesis chi cuadrado en temp y densidad.
OBS: Esta es la seleccion para las figuras 8 en adelante.

*Types of field lines
 I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

@@

\section{Results}\label{resu} 
\subsection{Tomographic Results}\label{demt_res}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ and $1.105\,\mrsun$, respectively. Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_demt_2082} but for CR-2208.}
\label{carmaps_demt_2208}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_updowntriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_updowntriple_gradt.eps}
\caption{Frequency histogram of the temperature radial gradient of along each leg of type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (left panel) and CR-2208 (right panel). In solid lines DEMT traced data and in dashed lines AWSoM data.}
\label{gradientes}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up.eps}
\caption{Average fitted of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082(top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $\NCB\equiv N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}

\label{histos_2082}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
\caption{Same as Figure \ref{histos_2082} but for CR2208.}
\label{histos_2208}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged of DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM.}
\label{perf_lon_vr}
\end{center}
\end{figure}
